CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-12-15 paper/ms.tex
Explain the velocity

\begin{equation}
y_{j,n}^{opt}=a\cdot y_{j-1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j+1,n}^{inf}
\end{equation}
\bigskip

@@

    1 & y_{1,n} ^{inf} & y_{2,n} ^{inf}\\
    y_{1,n}^{inf}&y_{2,n}^{inf}& y_{3,n}^{inf}  \\
    \vdots & \vdots & \vdots \\
    y_{J-1,n}^{inf}&y_{J,n}^{inf}& 1  \\

@@

The radial velocity is related to parameters a, b and c. First, we need to assume that the inferred spectrum generated by the Cannon is set at rest, which means the radial velocity of it is zero. Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the optimized spectrum. This is because the optimized spectrum is obtained by fitting the inferred spectrum to the data spectrum. 
\bigskip

To begin with, we set the radial velocity to be positive if the star is leaving us. If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift. Thus the radial velocity shift is negative and can be obtained by using (8). It's more convenient to use the logarithmic wavelength.
\begin{equation}
\log_{10}\lambda_0 - \log_{10}\lambda_s = \log_{10}(1+\beta)
\end{equation}

All spectrums in Apstar files are set to the same wavelength scale. The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$. By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if the data spectrum moves one pixel left, the radial velocity shift in the APOGEE data is $-4144.68 m/s$. 
\\ In the following formulas, $v_{shift}$ is the shift of the radial velocity in APOGEE data and $v_{pixel}$ =  4144.68 m/s, which is the radial velocity related to one pixel. $v_{light}$ is the speed of light.

We can use a, b and c to determine the radial velocity shift for the combined spectrum and each visit of the APOGEE data.
If the parameters are a, b and c, $a\over{a+b+c}$ of the spectrum moves one pixel left, $c\over{a+b+c}$ of the spectrum moves one pixel right and $b\over{a+b+c}$ of the spectrum doesn't move. The spectrum moves one pixel left has $v_{shift} = -v_{pixel}$ and the one moves one pixel right has $v_{shift} = v_{pixel}$. ${a+c}\over2$ of the spectrum is broadening but it's included in the spectrum moves left and right. Thus the data spectrum moves ${c-a}\over{(a+b+c)}$ pixel right and we have

\begin{equation}
\log_{10} (1+{v_{shift}}/v_{light}) = {{c-a}\over{(a+b+c)}}*\log_{10}(1+{v_{pixel}}/v_{light})
\end{equation}

$v_{shift}/v_{light}$ and $v_{pixel}/v_{light}$ are small so we can use Taylor expansion. Then we have:

\begin{equation}
v_{shift} = {{(c-a)*v_{pixel}}\over{a+b+c}}
\end{equation}

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_7.png}
\end{center}

$v_cc$ is the velocity shift from the cross-correlation. $v_David$ is the velocity shift from David's formula. $v_Jason$ is the velocity shift from Jason's formula.

\centerline{Diagnostic Fig.7 $v_cc$ vs$v_David$}

\begin{center}
\includegraphics[width=170mm]{d_figure_8.png}
\end{center}

\centerline{Diagnostic Fig.8 $v_cc$ vs$v_Jason$}

\begin{center}
\includegraphics[width=170mm]{d_figure_9.png}
\end{center}

\centerline{Diagnostic Fig.9 $v_cc$ vs$v_David$}

\begin{center}
\includegraphics[width=170mm]{d_figure_10.png}
\end{center}

\centerline{Diagnostic Fig.10 $v_cc$ vs$v_Jason$}

>>>>

\begin{equation}
y_{j,n}^{opt}=a\cdot y_{j+1,n}^{inf}+b\cdot y_{j,n}^{inf}+c\cdot y_{j-1,n}^{inf}
\end{equation}
\bigskip

@@

    y_{1,n}^{inf} & y_{1,n} ^{inf} & 1\\
    y_{2,n}^{inf}&y_{2,n}^{inf}& y_{2,n}^{inf}  \\
    \vdots & \vdots & \vdots \\
    1 &y_{J,n}^{inf}&  y_{J-1,n}^{inf} \\

@@

The radial velocity is related to parameters a, b and c. First, we need to assume that the inferred spectrum generated by the Cannon is set at rest, which means the radial velocity of it is zero. Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the optimized spectrum. This is because the optimized spectrum is obtained by fitting the inferred spectrum to the data spectrum. We set the radial velocity to be positive if the star is leaving us. 
\bigskip

The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift.

\begin{equation}
pixel_c = {\sum_{j=1}^{j=J} {j*y_{jn}}\over\sum_{j=1}^{j=J} {y_{jn}}}
\end{equation}

Where j is the pixel j, $y_{jn}$ is the flux at pixel j for star n. $pixel_c$ is the spectral centroid in pixel.

If the parameters are a, b and c. Then the centroid of the spectrum in frequency is:
\begin{equation}
pixel_c = {\sum_{j=1}^{j=J} {j*(a*y_{j+1,n}+b*y_{j,n}+c*y_{j-1,n})}\over\sum_{j=1}^{j=J} {(a*y_{j+1,n}+b*y_{j,n}+c*y_{j-1,n})}}
\end{equation}

We have $\sum_{j=1}^{j=J}{y_{j-1,n}}$ = $\sum_{j=1}^{j=J}{y_{j,n}}$ =$\sum_{j=1}^{j=J}{y_{j+1,n}}$ and $\sum_{j=1}^{j=J}{(j-1)*y_{j-1,n}}$ = $\sum_{j=1}^{j=J}{j*y_{j,n}}$ =$\sum_{j=1}^{j=J}{(j+1)*y_{j+1,n}}$. So the formula can be expressed as:

\begin{equation}
pixel_c = {\sum_{j=1}^{j=J} {j*(a*y_{j,n}+b*y_{j,n}+c*y_{j,n})}\over\sum_{j=1}^{j=J} {(a*y_{j,n}+b*y_{j,n}+c*y_{j,n})}} + {\sum_{j=1}^{j=J} {(c-a)*y_{j,n}}\over\sum_{j=1}^{j=J} {(a*y_{j,n}+b*y_{j,n}+c*y_{j,n})}}
\end{equation}

The first term is the centroid of the inferred flux. The second term is the shift of the centroid, which is:

\begin{equation}
pixel_c^{shift} = {{c-a}\over{a+b+c}}
\end{equation}

Thus we have:

\begin{equation}
RV_{shift} = pixel_c^{shift}\cdot v_{pixel}
\end{equation}
Where $RV_{shift} $ is the radial velocity shift and $pixel_c^{shift}$ is the pixel centroid shift between the two spectrum.

But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixel left or right can't be ignored. When this happen, we will use five parameters, which are:

@@
